### 2023-05-07 Draft.Rmd
Additional Rmd changes after comparing to the google docs for final revision changes

On the face of it, pronounced individual differences in unconscious processing effects on cognition seem possible, even likely. Indeed, previous investigations revealed heterogeneity in susceptibility to the attentional blink [@martens2006a], in the effects of stimulus onset asynchrony (SOA) on metacontrast masking [@albrecht2010a], and in the effects of visual imagery on conscious perception in a binocular rivalry setting [@dijkstra2019a]. Some qualitative differences have been linked to variability in processing speed [@martens2006a], genetics [@maksimov2013a], and brain anatomy and physiology [@gaal2011a; @boy2010a]. Critically, in other behavioural paradigms, unconscious stimuli had opposite effects on different participants. Bolger et al. [-@bolger2019a] showed that while the vast majority of participants responded faster to upright faces in a breaking continuous flash suppression task (b-CFS; @jiang2007a), some responded faster to upside-down faces. Other studies found that priming effects changed in magnitude and even flipped in sign as a function of SOA and visibility [@schlaghecken2004a; @boy2014a]. On the other hand, in other studies individual differences in prime visibility were not correlated with the magnitude of priming effects (@albrecht2010a; @boy2014a; but see @eimer2002a). Taken together, it is not clear if, and to what extent, unconscious effects are subject to meaningful individual variability. If they do, then some previously reported null results might actually be true effects, masked by such variability.

@@

To demonstrate how true causal effects of unconscious processing can be masked by inter-individual differences in effect signs, we simulated a typical experiment using a within-participants manipulation  (Figure 1). Specifically, we generated trial-by-trial data from a standard unconscious priming experiment. For each simulated participant, we generated reaction time data from two conditions (corresponding to congruent and incongruent primes in unconscious processing studies). Individual-level effect sizes (in milliseconds) were sampled from a normal distribution centred at zero ($e_{i} \sim {\mathcal{N}}(0, \sigma_{b})$, where $e_{i}$ denotes the true effect size of the ith participant and ($\sigma_b$) the between-participant standard deviation. Then, the trial-by-trial reaction times (RTs) of each participant and condition were generated according to each participant''s true effect score ($e_{i}$), the relevant condition ($c \in \{1, 0\}$, where $c=1$ denotes the incongruent condition, and $c=0$ denotes the congruent condition), and the within-participant standard deviation ($\sigma_{w}$) ($RT_{i,c} \sim {\mathcal{N}} (0, \sigma_{w}) +c*e_{i}$).
In two simulations, we manipulated two factors: the between-participant SD over effect sizes ($\sigma_{b}$), and the within-participant standard deviation (SD) over RTs within each condition ($\sigma_{w}$). This resulted in two distinct scenarios under this framework: (1) a *qualitative or non-directional differences scenario*, where all individuals show an effect, but individual-level effects largely vary in magnitude and sign  ($\sigma_{b}$=`r nde_sd_b`, $\sigma_{w}$=`r nde_sd_w`; Figure 1B)), and (2) a *global null* scenario [@allefeld2016a; @nichols2005a], where no single participant is affected by the experimental manipulation ($\sigma_{b}$=`r sn_sd_b`, $\sigma_{w}$= `r sn_sd_w`; Figure 1C). We simulated $N_{t}$=`r 2*sn_trials` trials from $N_{p}$=`r sn_n`  per scenario, noting that the general principle holds for other sample sizes and number of trials.

@@

We applied the tests to our simulated data, using the default priors from the original publications [@ince2021a; @rouder2021a], and an implementation of the ANOVA model underlying the OANOVA test (@miller2018a; see ([https://github.com/mufcItay/NDT](https://github.com/mufcItay/NDT)) for an R based implementation of the test). We considered $BF>`r bf_criteria`$ as evidence for an effect, $BF< \frac{1}{`r bf_criteria`}$ as evidence for no effect (*global null*), and values between these thresholds ($\frac{1}{`r bf_criteria`}\leq BF\leq `r bf_criteria`$) as inconclusive [@jeffreys1998a], and used an  $\alpha$ of `r oanova_alpha` for the OANOVA test. Reassuringly, all tests were able to differentiate between the two simulated scenarios, providing very strong evidence for an effect in the *non-directional differences* scenario, but not in the *global null* one. Specifically, According to PBT, about half of the population was estimated to show an effect of congruency on RT in the *non-directional differences* simulation (using a two-sided t-test for the individual-level test; $HDI_{95}$= [`r round(100*nde_pbt_res$low, 0)`, `r round(100*nde_pbt_res$high,0)`], $MAP$=`r round(100*nde_pbt_res$MAP,)`%; the 95% highest density interval and maximum a posteriori, respectively), but this proportion was not reliably different from zero in the *global null* simulation ($HDI_{95}$= [`r round(100*sn_pbt_res$low,0)`, `r round(100*sn_pbt_res$high,0)`], $MAP$= `r round(100*sn_pbt_res$MAP,0)`%). Using the QUID method, a random effects model with individual-level effects was overwhelmingly preferred in the *non-directional differences* simulation ($BF$= `r formatC(nde_bf, format = 'e', 2)`), but a null model was preferred in the *global null* simulation ($BF$= `r round(sn_bf,2)`). Similarly, the OANOVA test revealed significant results in the *non-directional differences* scenario (F(`r nde_OANOVA_res$df_num`, `r nde_OANOVA_res$df_denom`) = `r round(nde_OANOVA_res$F,2)`, p `r paste0(ifelse(nde_OANOVA_res$p >= .001, '=', ''), apa_p(nde_OANOVA_res$p))`), and a nonsignificant effect in the *global null* simulation (F(`r sn_OANOVA_res$df_num`, `r sn_OANOVA_res$df_denom`) = `r round(sn_OANOVA_res$F,2)`, p `r paste0(ifelse(sn_OANOVA_res$p >= .001, '=', ''),apa_p(sn_OANOVA_res$p))`).

@@

To examine whether inter-individual differences masked true unconscious priming effects in previously reported studies, we collected and tested data from eight studies that reported null results (@biderman2018a; @faivre2014a; @stein2021a; @zerweck2021a; @benthien2021a; @hurme2020a; @skora2021a; @chien2022a; all datasets and analysis scripts are publicly available online: [https://github.com/mufcItay/NDT](https://github.com/mufcItay/NDT)). 
We collected data associated with `r n_empiric_ns` null effects (see Supplementary Table 1 for details about all effects), 19 focusing on differences in RT and 7 on differences in signal detection sensitivity, d’ [@green1966a]. We used the criteria set by the original authors for demonstrating unawareness (e.g., using objective and/or subjective measures of awareness), and a two-sided non-parametric sign-flipping test for filtering out significant priming effects^[Across all RT effects, our analysis used raw RT scores, and thus our results diverged from the original results when log transformations were used (see the notes column in Supplementary Table 1 for details)]. Finally, we excluded participants with fewer than five trials per experimental condition and/or zero variance in the dependent variable (e.g., when accuracy was measured). Together, these data allowed us to reexamine null unconscious processing effects using a non-directional approach that takes into account the potential for difference in effect signs when testing for group-level effects. We accordingly asked whether true effects of unconscious processing were masked by population heterogeneity in effect signs.
To that end, the effects of interest were tested using PBT, QUID, and the OANOVA tests (see Supplementary Figure 1 for an analysis of the significant directional effects which were excluded). PBT was applied to all `r n_empiric_ns` effects. In contrast, QUID and OANOVA were used on subsets of `r n_empiric_ns_quid` and `r n_empiric_ns_oanova` of these effects, respectively (omitting five effects of signal detection sensitivity, d’, from both tests, and one additional RT interaction from the QUID analysis, as its current implementation supports simple RT effects only).
All tests agreed on finding no reliable evidence for non-directional unconscious effects. According to PBT, the MAP prevalence statistic was zero in `r round(100*p_pbt_MAP_zero,2)`% of the effects (maximal $MAP$ = `r ns_pbt_res %>% filter(is_sim == FALSE) %>% mutate(map=round(100*pbt.MAP, 2)) %>% pull(map) %>% max()`%; see Fig. 2A), and the 95% HDI included zero in all of them. Similarly, for both QUID and the OANOVA tests, no single $BF$ or p-value revealed evidence for an effect (maximal $BF_{10}$ = `r formatC(ns_quid_res %>% filter(is_sim == FALSE) %>% pull(quid_bf) %>% max(), format = 'e', 2)` and all p-values > `r oanova_alpha`; see Figure 2B,C). Notably, QUID obtained moderate evidence for the *global null* model in `r round(100*p_null_QUID,2)`% of the cases (see Fig. 2B). The remaining effects were inconclusive. Hence, for the effects collected here, in the case of unconscious processing, the three tests revealed a highly similar pattern of results, consistent with a strong interpretation of previously reported null results as revealing the genuine absence of a causal effect of unconsciously perceived stimuli on behaviour.

(ref:figure2caption) The results of applying the PBT (A), QUID (B), and OANOVA (C) tests to effects that produced null results in a non-parametric directional test (N = `r n_empiric_ns`, N = `r n_empiric_ns_quid`, and N = `r n_empiric_ns_oanova` for (A), (B) and (C), respectively) and to simulated data (the Non-directional effect (ND) and Global Null (GN) simulations described above, presented on the left, marked by a purple background and square shaped markers). Effect labels^[Effect labels abbreviations (sorted alphabetically): BH = @benthien2021a, BM = @biderman2018a, C = @chien2022a, F = @faivre2014a, H = @hurme2020a, S = @skora2021a, SV = @stein2021a, Z = @zerweck2021a. For all labels, numbers denote effect indices within each study (see Supplementary Table 1 for the full mapping between labels and effects).] appear on the x-axis. Panel A: the estimated prevalence of an unconscious effect in each of the cases, using PBT [@ince2021a]. Markers indicate the maximum a posteriori ($MAP$) for each of the effects, and segments depict the 95% highest density interval ($HDI_{95}$). Grey markers depict above-zero MAPs. For all effects, the lower bound of the HDI95 was zero, indicating that the global null is plausible, even when the MAP is above zero. Panel B: Bayes factors for the comparison between a random effects model that takes into account potential differences in effect signs and the global null model. White markers depict cases where moderate evidence for the  *global null* model. White markers depict cases where moderate evidence for the global null model was found, while grey markers indicate inconclusive results. The dashed black line indicates a BF of 1 (no preference for either model), and the solid orange lines indicate a BF cutoff of `r bf_criteria`. Panel C: p-values obtained by the OANOVA test [miller2018a]. Blue and grey markers indicate significant and non-significant results, respectively. For illustration purposes, BF and significance values are presented on a logarithmic scale on the y axis.
```{r figure2, out.width="100%", fig.cap = "(ref:figure2caption)"}
knitr::include_graphics("figures//plots//ns_available_methods_res.png")
```

@@

We used the sign-consistency test to expose hidden effects that were not revealed by standard directional tests in various fields of research. We collected data from different open-access databases (the Confidence Database [@rahnev2020a], the Reproducibility Project [collaboration2015a], and the Classic Visual Search Effects open dataset [@adam2021a]). We also used social media to ask for previously reported null effects. We had two inclusion criteria: first, to estimate subject-level sign-consistency, the independent variable had to be manipulated within single participants. And second, we filtered out effects that were significant in a non-parametric, directional test. Overall, we collected data associated with `r N_ns_no_UC` nonsignificant effects (`r N_ns_Confidence` from the Confidence Database, `r apa_num(as.integer(N_ns_Reproducibility), numerals = FALSE)` from the Reproducibility Project, `r apa_num(as.integer(N_ns_Attention), numerals = FALSE)` from the Classic Visual Search Effects open dataset and `r apa_num(as.integer(N_ns_Social),numerals = FALSE)` from the social media query). In all cases, participants were excluded for having fewer than five trials per experimental condition and/or zero variance in the dependent variable. 

@@

Overall, in two out of`r n_empiric_ns` effects, a sign-consistency test detected an effect that was missed by a standard, directional test. However, even these two effects should be examined cautiously. The effect found for the third experiment in Biderman & Mudrik [-@biderman2018a] (M = `r round(100* bm_3_res %>% pull(signcon.statistic) %>% first(),0)`%, p = `r apa_p(bm_3_res %>% pull(signcon.p) %>% first())`) was not detected by the three other tests and did not survive a correction for false discovery rate among unconscious processing effects [@benjamini1995a]. Hence, it is likely that this effect reflects a type-1 error. Similarly, while we found significant sign-consistency (M = `r round(100* skora_1_res %>% pull(signcon.statistic) %>% first(),0)`%, p = `r apa_p(skora_1_res %>% pull(signcon.p) %>% first())`) for a d' effect in the first experiment of Skora et al., [-@skora2021a], PBT provided no evidence for an above-zero prevalence (we only used PBT and sign-consistency to examine this effect, since QUID focuses on RT effects and the OANOVA test does not model effects which are measured across multiple trials). Importantly, the authors expressed concerns regarding possible contamination of their measured effect by conscious processing due to regression to the mean [@shanks2017a]. Thus, we suggest that our findings should be interpreted as suggesting no masking of unconscious processing effects by population heterogeneity.

@@

\newpage
# Supplementary Table 1 {#STable-1}
``` {r supptable-1}
# create the supplementary table by code
Study <- c('Biderman & Mudrik, 2018', 'Faivre et al., 2014', 'Stein & Peelen, 2021', 
'Zerweck et al., 2021', 'Benthien & Hesselmann, 2021', 'Hurme et al., 2020', 
'Skora et al., 2021', 'Chien et al., 2022')
Labels <- c('BM1-3', 'F1-8', 'SVP1-5','Z1-7','BH1','H1-4','S1-2','C1-3')
Topic <- c('Scene congruency', 'Multisensory integration', 'Location effects + PAS (detection)',
'Numerical Priming', 'Numerical Priming', 'Colors', 'Instrumental Learning', 'Semantic priming')
Paradigm <- c('Masking', 'Masking', 'CFS', 'Masking', 'CFS', 'TMS + Metacontrast Masking', 'Masking', 'CFS')
DV <- c('RT', 'RT', 'd\'', 'RT', 'RT', 'RT', 'd\'', 'RT')
Notes <- c('Replication study. For all experiments, log(RT) was used in the original analysis',
'Four experiments, two effects in each experiment (identical/different targets). For all experiments, log(RT) was used in the original analysis',
'Two experiments (3&4 in the paper), measuring effects in different prime-mask SOAs',
'Two experiments (2 and 3 in the original paper), measuring effects in different SOA / Contrast conditions',
'Interaction effect - prime congruency X location certainty',
'Redundant target effect (TMS / Masking X Blue / Red)',
'Regression to the mean as a confound according to authors',
'Word, Picture, and trait discrimination tasks')
studies_df <- data.frame(Study, Labels, Topic, DV, Notes)
# print the table according to apa style using a small font size
apa_table(
  studies_df,
  caption = "Unconscious processing effects metadata",
  font_size = 'footnotesize')
```

@@

We used the simulation scheme described in the main text (see section ‘Simulating non-directional unconscious effects’), to test the consequences of violating the equal within-individuals variance assumption for both QUID and the OANOVA test. We compared the distribution of Bayes factors and p-values obtained by applying QUID and the OANOVA test to generated data meeting and violating the equal within-participants variance assumption. In the first, equal-variance case, the within-individual standard deviation was low ($\sigma_{w}=`r apndxA_sigma_w_low`$) for all participants. In the second, unequal-variance case, the within-individual standard deviation was low ($\sigma_{w}=`r apndxA_sigma_w_low`$) for all participants except one, for whom it was set to a high value ($\sigma_{w}=`r apndxA_sigma_w_unequal`$). As in the main simulation, effect sizes of each participant were sampled from a normal distribution centered at zero ($e_{i} \sim {\mathcal{N}}(`r apndxA_mu`, \sigma_{b})$; where $e_{i}$ denotes the effect size of the ith participant). Within this framework, examined two scenarios: a non-directional differences scenario where participants are differentially affected by the experimental manipulation ($N_{p}=`r apndxA_sensitivity_Np`$, $\sigma_{b}=`r apndxA_sensitivity_sigma_b`$), and a global null condition where all participants are unaffected by the experimental manipulation ($N_{p}=`r apndxA_FA_Np`$, $\sigma_{b}=`r apndxA_FA_sigma_b`$). In both scenarios, we simulated random data in `r apndxA_iterations` iterations, and used the same number of trials per condition (the total number of trials, $N_{t}= `r apndxA_Nt`$).

>>>>

On the face of it, pronounced individual differences in unconscious processing effects on cognition seem possible, even likely. Indeed, previous investigations revealed heterogeneity in susceptibility to the attentional blink [@martens2006a], in the effects of stimulus onset asynchrony (SOA) on metacontrast masking [@albrecht2010a], and in the effects of visual imagery on conscious perception in a binocular rivalry setting [@dijkstra2019a]. Some qualitative differences have been linked to variability in processing speed [@martens2006a], genetics [@maksimov2013a], and brain anatomy and physiology [@gaal2011a; @boy2010a]. Critically, in other behavioural paradigms, unconscious stimuli had opposite effects on different participants. Bolger et al. [-@bolger2019a] showed that while most participants responded faster to upright faces in a breaking continuous flash suppression task (b-CFS; @jiang2007a), some responded faster to upside-down faces. Other studies found that priming effects changed in magnitude and even flipped in sign as a function of SOA and visibility [@schlaghecken2004a; @boy2014a]. On the other hand, in other studies individual differences in prime visibility were not correlated with the magnitude of priming effects (@albrecht2010a; @boy2014a; but see @eimer2002a). Taken together, it is not clear if, and to what extent, unconscious effects are subject to meaningful individual variability. If they do, then some previously reported null results might actually be true effects, masked by such variability.

@@

To demonstrate how true causal effects of unconscious processing can be masked by inter-individual differences in effect signs, we simulated a typical experiment using a within-participants manipulation  (Figure 1). Specifically, we generated trial-by-trial data from a standard unconscious priming experiment. For each simulated participant, we generated reaction time data from two conditions (corresponding to congruent and incongruent primes in unconscious processing studies). Individual-level effect sizes (in milliseconds) were sampled from a normal distribution centred at zero ($e_{i} \sim {\mathcal{N}}(0, \sigma_{b})$, where $e_{i}$ denotes the true effect size of the ith participant and ($\sigma_b$) the between-participant standard deviation. Then, the trial-by-trial reaction times (RTs) of each participant and condition were generated according to each participant's true effect score ($e_{i}$), the relevant condition ($c \in \{1, 0\}$, where $c=1$ denotes the incongruent condition, and $c=0$ denotes the congruent condition), and the within-participant standard deviation ($\sigma_{w}$) ($RT_{i,c} \sim {\mathcal{N}} (0, \sigma_{w}) +c*e_{i}$).
In two simulations, we manipulated two factors: the between-participant SD over effect sizes ($\sigma_{b}$), and the within-participant standard deviation (SD) over RTs within each condition ($\sigma_{w}$). This resulted in two distinct scenarios under this framework: (1) a *qualitative or non-directional differences scenario*, where all individuals show an effect, but individual-level effects largely vary in magnitude and sign  ($\sigma_{b}$=`r nde_sd_b`, $\sigma_{w}$=`r nde_sd_w`; Figure 1B)), and (2) a *global null* scenario [@allefeld2016a; @nichols2005a], where no single participant is affected by the experimental manipulation ($\sigma_{b}$=`r sn_sd_b`, $\sigma_{w}$= `r sn_sd_w`; Figure 1C). We simulated $N_{t}$=`r 2*sn_trials` trials from $N_{p}$=`r sn_n` participants per scenario, noting that the general principle holds for other sample sizes and number of trials.

@@

We applied the tests to our simulated data, using the default priors from the original publications [@ince2021a; @rouder2021a], and an implementation of the ANOVA model underlying the OANOVA test (@miller2018a; see ([https://github.com/mufcItay/NDT](https://github.com/mufcItay/NDT)) for an R based implementation of the test). For PBT, we examined whether the lower bound of the prevalence $HDI_{95}$ exceeded zero. We considered $BF>`r bf_criteria`$ as evidence for an effect, $BF< \frac{1}{`r bf_criteria`}$ as evidence for no effect (*global null*), and values between these thresholds ($\frac{1}{`r bf_criteria`}\leq BF\leq `r bf_criteria`$) as inconclusive [@jeffreys1998a], and used an  $\alpha$ of `r oanova_alpha` for the OANOVA test. Reassuringly, all tests were able to differentiate between the two simulated scenarios, providing very strong evidence for an effect in the *non-directional differences* scenario, but not in the *global null* one. Specifically, According to PBT, about half of the population was estimated to show an effect of congruency on RT in the *non-directional differences* simulation (using a two-sided t-test for the individual-level test; $HDI_{95}$= [`r round(100*nde_pbt_res$low, 0)`, `r round(100*nde_pbt_res$high,0)`], $MAP$=`r round(100*nde_pbt_res$MAP,)`%; the 95% highest density interval and maximum a posteriori, respectively), but this proportion was not reliably different from zero in the *global null* simulation ($HDI_{95}$= [`r round(100*sn_pbt_res$low,0)`, `r round(100*sn_pbt_res$high,0)`], $MAP$= `r round(100*sn_pbt_res$MAP,0)`%). Using the QUID method, a random effects model with individual-level effects was overwhelmingly preferred in the *non-directional differences* simulation ($BF$= `r formatC(nde_bf, format = 'e', 2)`), but a null model was preferred in the *global null* simulation ($BF$= `r round(sn_bf,2)`). Similarly, the OANOVA test revealed significant results in the *non-directional differences* scenario (F(`r nde_OANOVA_res$df_num`, `r nde_OANOVA_res$df_denom`) = `r round(nde_OANOVA_res$F,2)`, p `r paste0(ifelse(nde_OANOVA_res$p >= .001, '=', ''), apa_p(nde_OANOVA_res$p))`), and a nonsignificant effect in the *global null* simulation (F(`r sn_OANOVA_res$df_num`, `r sn_OANOVA_res$df_denom`) = `r round(sn_OANOVA_res$F,2)`, p `r paste0(ifelse(sn_OANOVA_res$p >= .001, '=', ''),apa_p(sn_OANOVA_res$p))`).

@@

To examine whether inter-individual differences masked true unconscious priming effects in previously reported studies, we collected and tested data from eight studies that reported null results (@biderman2018a; @faivre2014a; @stein2021a; @zerweck2021a; @benthien2021a; @hurme2020a; @skora2021a; @chien2022a; all datasets and analysis scripts are publicly available online: [https://github.com/mufcItay/NDT](https://github.com/mufcItay/NDT)). 
We collected data associated with `r n_empiric_ns` null effects (see Supplementary Table 1 for details about all effects), 19 focusing on differences in RT and 7 on differences in signal detection sensitivity, d’ [@green1966a]. We used the criteria set by the original authors for demonstrating unawareness (e.g., using objective and/or subjective measures of awareness), and a two-sided non-parametric sign-flipping test for filtering out significant priming effects^[Across all RT effects, our analysis used raw RT scores, and thus our results diverged from the original results when log transformations were used (see the notes column in Supplementary Table 1 for details)]. Finally, we excluded participants with fewer than five trials per experimental condition and/or zero variance in the dependent variable (e.g., when accuracy was measured). Together, these data allowed us to reexamine null unconscious processing effects using a non-directional approach that takes into account the potential for difference in effect signs when testing for group-level effects. We accordingly asked whether true effects of unconscious processing were masked by population heterogeneity in effect signs.
To that end, the effects of interest were tested using PBT, QUID, and the OANOVA tests (see Supplementary Figure 1 for an analysis of the significant directional effects which were excluded). PBT was applied to all `r n_empiric_ns` effects. In contrast, QUID and OANOVA were used on subsets of `r n_empiric_ns_quid` and `r n_empiric_ns_oanova` of these effects, respectively (omitting five effects of signal detection sensitivity, d’, from both tests, and one additional RT interaction from the QUID analysis, as its current implementation supports simple RT effects only).
All tests agreed on finding no reliable evidence for non-directional unconscious effects. According to PBT, the MAP prevalence statistic was zero in `r round(100*p_pbt_MAP_zero,2)`% of the effects (maximal $MAP$ = `r ns_pbt_res %>% filter(is_sim == FALSE) %>% mutate(map=round(100*pbt.MAP, 2)) %>% pull(map) %>% max()`%; see Fig. 2A), and the 95% HDI included zero in all of them. Similarly, for both QUID and the OANOVA tests, no single $BF$ or p-value revealed evidence for an effect (maximal $BF_{10}$ = `r round(ns_quid_res %>% filter(is_sim == FALSE) %>% pull(quid_bf) %>% max(), 2)` and all p-values > `r oanova_alpha`; see Figure 2B,C). Notably, QUID obtained moderate evidence for the *global null* model in `r round(100*p_null_QUID,2)`% of the cases (see Fig. 2B). The remaining effects were inconclusive. Hence, for the effects collected here, in the case of unconscious processing, the three tests revealed a highly similar pattern of results, consistent with a strong interpretation of previously reported null results as revealing the genuine absence of a causal effect of unconsciously perceived stimuli on behaviour.

(ref:figure2caption) The results of applying the PBT (A), QUID (B), and OANOVA (C) tests to effects that produced null results in a non-parametric directional test (N = `r n_empiric_ns`, N = `r n_empiric_ns_quid`, and N = `r n_empiric_ns_oanova` for (A), (B) and (C), respectively) and to simulated data (the Non-directional effect (ND) and Global Null (GN) simulations described above, presented on the left, marked by a purple background and square shaped markers). Effect labels^[Effect labels abbreviations (sorted alphabetically): BH = @benthien2021a, BM = @biderman2018a, C = @chien2022a, F = @faivre2014a, H = @hurme2020a, S = @skora2021a, SV = @stein2021a, Z = @zerweck2021a. For all labels, numbers denote effect indices within each study (see Supplementary Table 1 for the full mapping between labels and effects).] appear on the x-axis. Panel A: the estimated prevalence of an unconscious effect in each of the cases, using PBT [@ince2021a]. Markers indicate the maximum a posteriori ($MAP$) for each of the effects, and segments depict the 95% highest density interval ($HDI_{95}$). Grey markers depict above-zero MAPs. For all effects, the lower bound of the HDI95 was zero, indicating that the global null is plausible, even when the MAP is above zero. Panel B: Bayes factors for the comparison between a random effects model that takes into account potential differences in effect signs and the global null model. White markers depict cases where moderate evidence for the global null model was found, while grey markers indicate inconclusive results. The dashed black line indicates a BF of 1 (no preference for either model), and the solid orange lines indicate a BF cutoff of `r bf_criteria`. Panel C: p-values obtained by the OANOVA test [@miller2018a]. Blue and grey markers indicate significant and non-significant results, respectively. For illustration purposes, BF and significance values are presented on a logarithmic scale on the y axis.
```{r figure2, out.width="100%", fig.cap = "(ref:figure2caption)"}
knitr::include_graphics("figures//plots//ns_available_methods_res.png")
```

@@

We used the sign-consistency test to expose hidden effects that were not revealed by standard directional tests in various fields of research. We collected data from different open-access databases (the Confidence Database [@rahnev2020a], the Reproducibility Project [@collaboration2015a], and the Classic Visual Search Effects open dataset [@adam2021a]). We also used social media to ask for previously reported null effects. We had two inclusion criteria: first, to estimate subject-level sign-consistency, the independent variable had to be manipulated within single participants. And second, we filtered out effects that were significant in a non-parametric, directional test. Overall, we collected data associated with `r N_ns_no_UC` nonsignificant effects (`r N_ns_Confidence` from the Confidence Database, `r apa_num(as.integer(N_ns_Reproducibility), numerals = FALSE)` from the Reproducibility Project, `r apa_num(as.integer(N_ns_Attention), numerals = FALSE)` from the Classic Visual Search Effects open dataset and `r apa_num(as.integer(N_ns_Social),numerals = FALSE)` from the social media query). In all cases, participants were excluded for having fewer than five trials per experimental condition and/or zero variance in the dependent variable. 

@@

Overall, in two out of `r n_empiric_ns` effects, a sign-consistency test detected an effect that was missed by a standard, directional test. However, even these two effects should be examined cautiously. The effect found for the third experiment in Biderman & Mudrik [-@biderman2018a] (M = `r round(100* bm_3_res %>% pull(signcon.statistic) %>% first(),0)`%, p = `r apa_p(bm_3_res %>% pull(signcon.p) %>% first())`) was not detected by the three other tests and did not survive a correction for false discovery rate among unconscious processing effects [@benjamini1995a]. Hence, it is likely that this effect reflects a type-1 error. Similarly, while we found significant sign-consistency (M = `r round(100* skora_1_res %>% pull(signcon.statistic) %>% first(),0)`%, p = `r apa_p(skora_1_res %>% pull(signcon.p) %>% first())`) for a d' effect in the first experiment of Skora et al., [-@skora2021a], PBT provided no evidence for an above-zero prevalence (we only used PBT and sign-consistency to examine this effect, since QUID focuses on RT effects and the OANOVA test does not model effects which are measured across multiple trials). Importantly, the authors expressed concerns regarding possible contamination of their measured effect by conscious processing due to regression to the mean [@shanks2017a]. Thus, we suggest that our findings should be interpreted as suggesting no masking of unconscious processing effects by population heterogeneity.

@@

\newpage
# Supplementary Table 1 {#STable-1}
``` {r supptable-1}
# create the supplementary table by code
Study <- c('Biderman & Mudrik, 2018', 'Faivre et al., 2014', 'Stein & Peelen, 2021', 
'Zerweck et al., 2021', 'Benthien & Hesselmann, 2021', 'Hurme et al., 2020', 
'Skora et al., 2021', 'Chien et al., 2022')
Labels <- c('BM1-3', 'F1-8', 'SVP1-5','Z1-7','BH1','H1-4','S1-2','C1-3')
Topic <- c('Scene congruency', 'Multisensory integration', 'Location effects + PAS (detection)',
'Numerical Priming', 'Numerical Priming', 'Colors', 'Instrumental Learning', 'Semantic priming')
Paradigm <- c('Masking', 'Masking', 'CFS', 'Masking', 'CFS', 'TMS + Metacontrast Masking', 'Masking', 'CFS')
DV <- c('RT', 'RT', 'd\'', 'RT', 'RT', 'RT', 'd\'', 'RT')
Notes <- c('Replication study. For all experiments, log(RT) was used in the original analysis',
'Four experiments, two effects in each experiment (identical/different targets). For all experiments, log(RT) was used in the original analysis',
'Two experiments (3&4 in the paper), measuring effects in different prime-mask SOAs',
'Two experiments (2 and 3 in the original paper), measuring effects in different SOA / Contrast conditions',
'Interaction effect - prime congruency X location certainty',
'Redundant target effect (TMS / Masking X Blue / Red)',
'Regression to the mean as a confound according to authors',
'Word, Picture, and trait discrimination tasks')
studies_df <- data.frame(Study, Labels, Topic, Paradigm, DV, Notes)
# print the table according to apa style using a small font size
apa_table(
  studies_df,
  caption = "Unconscious processing effects metadata",
  font_size = 'footnotesize')
```

@@

We used the simulation scheme described in the main text (see section ‘Simulating non-directional unconscious effects’), to test the consequences of violating the equal within-individuals variance assumption for both QUID and the OANOVA test. We compared the distribution of Bayes factors and p-values obtained by applying QUID and the OANOVA test to generated data meeting and violating the equal within-participants variance assumption. In the first, equal-variance case, the within-individual standard deviation was low ($\sigma_{w}=`r apndxA_sigma_w_low`$) for all participants. In the second, unequal-variance case, the within-individual standard deviation was low ($\sigma_{w}=`r apndxA_sigma_w_low`$) for all participants except one, for whom it was set to a high value ($\sigma_{w}=`r apndxA_sigma_w_unequal`$). As in the main simulation, effect sizes of each participant were sampled from a normal distribution centered at zero ($e_{i} \sim {\mathcal{N}}(`r apndxA_mu`, \sigma_{b})$; where $e_{i}$ denotes the effect size of the ith participant). Within this framework, examined two scenarios: a *non-directional differences* scenario where participants are differentially affected by the experimental manipulation ($N_{p}=`r apndxA_sensitivity_Np`$, $\sigma_{b}=`r apndxA_sensitivity_sigma_b`$), and a *global null* condition where all participants are unaffected by the experimental manipulation ($N_{p}=`r apndxA_FA_Np`$, $\sigma_{b}=`r apndxA_FA_sigma_b`$). In both scenarios, we simulated random data in `r apndxA_iterations` iterations, and used the same number of trials per condition (the total number of trials, $N_{t}= `r apndxA_Nt`$).
